Ancestry linkage in hybrid zones

### 2016-02-10 drafts/hybrid_zone.tex
added some block length figures

We were interested in determining whether targets of selection could potentially be identified by a signal of larger ancestry tracts surrounding them compared to a genome-wide background. To demonstrate this, we simulated a chromosome of length 1M with a selected site at position 0.5M. For a set of positions along the chromosome, we computed the length of the surrounding unbroken block of ancestry. There is a detectable signal of increased block length surrounding selected loci, especially when conditioning on the less-fit ancestry (FigureX) at geographic sites far from the center of the zone.

>>>>

Of particular interest is whether or targets of selection could potentially be identified by a signal of larger ancestry tracts surrounding them compared to a genome-wide background. To demonstrate this, we simulated a chromosome of length 1M with a selected site at position 0.5M. For a set of positions along the chromosome, we computed the length of the surrounding unbroken block of ancestry. There is a detectable signal of increased block length surrounding selected loci, especially when conditioning on the less-fit ancestry (FigureX) at geographic sites far from the center of the zone.
